Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-06-26 edubots_surveys.Rnw
added xgboost results figure

As the evaluation of all possible combinations might be unfeasible from a computational point of view, the following heuristic was applied: rank the variables using the MI of that variable isolatedly, apply a threshold to discard the ones with smaller MI and then, make a exhaustive search for the combination with higher MI.

\begin{tabular}{|c|c|c|c|c|}
\hline
\# Variable & Name & MI (considering one variable) & Max Relevance & mRMR\\
\hline
0 & AgendaBot	&  &  &\\
1 & ClassMaterialBot &	&  &	\\
2 & Age	&		&  &  \\
3 & Experience &			&  &  	\\
4 & FAQBot &			&  &  	\\
5 & GradesBot &			&  &  	\\
6 & Gender &			&  &  	\\
7 & MessagingPlatform0ne &			&  &  	\\
8 & MessagingPlatformOther &			&  &  	\\
9 & MessagingPlatformProvided	&			&  &  \\
10 & MessagingPlatformSlack	&			&  &  \\
11 & MessagingPlatformTelegram	&			&  &  \\
12 & MessagingPlatformWhatsApp	&			&  &  \\
13 & OtherBot	&			&  &  \\
14 & Sector	&			&  &  \\
15 & Messaging Organization → Number of approaches considered	&			&  &  \\
16 & Degrees → Number of degrees involved	&			&  &  \\
17 & Discipline	&		&  &  	\\
\hline
Output & \multirow{3}{PostCOVID changes} 	\\
\hline
\end{tabular} \label{tab:feature_reference} \caption{Mapping of feature numbers to survey questions.}
\end{table}

@@

Due to the lack of data, estimators based on $k$-Nearest Neighbours might be unreliable, thus, another approach can be used: decision trees build during their design process a relevance of the variables that, after being used to take the decision, decrease in a significant way the error. Therefore, the well known implementation of the XGBoost was used to obtain the accuracy and the feature relevance.

>>>>

As the evaluation of all possible combinations might be unfeasible from a computational point of view, the following heuristic was applied: rank the variables using the MI of that variable isolated, apply a threshold to discard the ones with smaller MI and then, make a exhaustive search for the combination with higher MI.

\begin{tabular}{|c|c|c|c|c|}
\hline
\# Variable & Name & MI (considering one variable) & Max Relevance & mRMR\\
\hline
0 & AgendaBot	&  &  &\\
1 & ClassMaterialBot &	&  &	\\
2 & Age	&		&  &  \\
3 & Experience &			&  &  	\\
4 & FAQBot &			&  &  	\\
5 & GradesBot &			&  &  	\\
6 & Gender &			&  &  	\\
7 & MessagingPlatform0ne &			&  &  	\\
8 & MessagingPlatformOther &			&  &  	\\
9 & MessagingPlatformProvided	&			&  &  \\
10 & MessagingPlatformSlack	&			&  &  \\
11 & MessagingPlatformTelegram	&			&  &  \\
12 & MessagingPlatformWhatsApp	&			&  &  \\
13 & OtherBot	&			&  &  \\
14 & Sector	&			&  &  \\
15 & Messaging Organization → Number of approaches considered	&			&  &  \\
16 & Degrees → Number of degrees involved	&			&  &  \\
17 & Discipline	&		&  &  	\\
\hline
Output & \multirow{3}{PostCOVID changes} 	\\
\hline
\end{tabular} \label{tab:feature_results} \caption{Mapping of feature numbers to survey questions.}
\end{table}

@@

Due to the lack of data, estimators based on $k$-Nearest Neighbours might be unreliable, thus, another approach can be used: decision trees build during their design process a relevance of the variables that, after being used to take the decision, decrease in a significant way the error. Therefore, the well known implementation of the XGBoost \cite{} was used to obtain the accuracy and the feature relevance.

The feature ranking results are shown in Figure \ref{fig:feature_xgboost}.
\begin{figure}
\includegraphics{figs/feature_xgboost.png}
\label{fig:feature_xgboost}\caption{Ranking of features obtained after using XGBoost model.}
\end{figure}
